### 2017-02-24 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1651 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
	title="Example of an html document with subfigures", 		
	author='Patrick Brown',
	slides=FALSE,
	bibliography = bibFile,
	geometry='margin=1in',
#	csl = system.file('src','apa-no-doi-no-issue.csl', package='Pmisc'),
	css = system.file('src','article.css', package='Pmisc')
)
```

@@

Here is a table

@@

tableFun = function(...) {
  if(mdToTex) {
    Hmisc::latex(...)
  } else {
    Hmisc::html(...)
  }
}
tableFun(mytable, digits=3, file='',
  caption = 'the table', caption.loc='bottom',
  label = 'tbl:theTable'
    )

>>>>

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
	title="Example of an html document with subfigures", 		
	author='Patrick Brown',
	slides=FALSE,
	bibliography = bibFile,
	geometry='margin=1in',
	csl = system.file('src','apa-no-doi-no-issue.csl', package='Pmisc'),
	css = system.file('src','article.css', package='Pmisc')
)
```

@@

Below one will find Table [@tbl:theTable]

@@

mdTable(x=mytable, digits=3,
  caption = 'the table', caption.loc='bottom')
